Are parental care induced gene expression patterns affect more by internal cues or external stimuli?

### 2019-09-06 docs/manipulation_manuscript.tex
need more resutls

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Are parental care induced gene expression patterns affect more by
internal cues or external stimuli?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rayna M Harris\textsuperscript{\getAff{UC Davis}}\textsuperscript{*},
Suzanne Austin\textsuperscript{\getAff{UC Davis}},
Andrew Lang\textsuperscript{\getAff{UNH}},
Matthew MacManes\textsuperscript{\getAff{UNH}},
Rebecca M Calisi\textsuperscript{\getAff{UC Davis}}\\
\bigskip
\textbf{\getAff{UC Davis}}UC Davis, Davis, CA\\
\textbf{\getAff{UNH}}UNH, smalltown, NH\\
\bigskip
* Corresponding author: rmharris@ucdavis\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
The one question saught. Here we do. What we found. How it matters.

@@

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Are parental care induced gene expression patterns affect more by
internal cues or external stimuli?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rayna M Harris\textsuperscript{\getAff{UC Davis}}\textsuperscript{*},
Suzanne Austin\textsuperscript{\getAff{UC Davis}},
Andrew Lang\textsuperscript{\getAff{UNH}},
Matthew MacManes\textsuperscript{\getAff{UNH}},
Rebecca M Calisi\textsuperscript{\getAff{UC Davis}}\\
\bigskip
\textbf{\getAff{UC Davis}}UC Davis, Davis, CA\\
\textbf{\getAff{UNH}}UNH, smalltown, NH\\
\bigskip
* Corresponding author: rmharris@ucdavis\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Are parental care induced gene expression patterns affect more by
internal cues or external stimuli? We test two alternative hypothesis:
internal clock cues versus external offspring stimuli by manipulating
the timing of normal transitions during parental care. When we removed
offpsring, we find the most pronounces chagnes in gene expression later
during incubation or right after hatch, compared to early removeal of
eggs. Given the similarity in gene expression the days immediately
preceeding and immedately following hatch, we do not have the power to
say weether gene expression patters are more like hatch or incuabtion
when dummmy egg are used to extend incubation. This matters
because\ldots{}

@@

\includegraphics{manipulation_manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}

\includegraphics{manipulation_manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
